### 2022-04-19 initialdraft.Rmd
first rmd file

---
title: "finalproj"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2022-04-19 initialdraft.Rmd
rmd setup

@@
 ---
-title: "finalproj"
-output: html_document
+title: 'finalproj'
+author: "Jocelyn, Ana, Cat"
+output: 
+  html_document:
+    keep_md: TRUE
+    toc: TRUE
+    toc_float: TRUE
+    df_print: paged
+    code_download: true
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
 ```
-
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
-```
-
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2022-04-19 initialdraft.Rmd
with options and data

@@
 ```
+
+```{r}
+library(dplyr)
+library(readr)
+library(ggplot2)
+library(gridExtra)
+library(tidyverse)
+```
+
+```{r}
+healthy_data <- read_csv("healthy_lifestyle_city_2021.csv", 
+    col_types = cols(Rank = col_number(), 
+        `Sunshine hours(City)` = col_number(), 
+        `Cost of a bottle of water(City)` = col_number(), 
+        `Obesity levels(Country)` = col_number(), 
+        `Life expectancy(years) (Country)` = col_number(), 
+        `Pollution(Index score) (City)` = col_number(), 
+        `Annual avg. hours worked` = col_number(), 
+        `Happiness levels(Country)` = col_number(), 
+        `Outdoor activities(City)` = col_number(),
+        `Number of take out places(City)` = col_number(), 
+        `Cost of a monthly gym membership(City)` = col_number()))
+```

### 2022-04-19 initialdraft.Rmd
converted to $

@@
         `Cost of a monthly gym membership(City)` = col_number()))
+
+# converting to dollars
+healthy_data_dollars <- healthy_data %>% 
+  mutate(water_bottle_cost = `Cost of a bottle of water(City)`*1.3,
+         gym_cost = `Cost of a monthly gym membership(City)`*1.3)
 ```

### 2022-04-19 initialdraft.Rmd
adding tidy tuesday graph

@@
 ```
+
+Which cities are the sunniest and least sunny?
+```{r, fig.alt = "Graph of the top 10 and bottom 10 cities by annual sunshine hours.The cities are mapped on the y-axis while the sunshine hours is mapped on the x-axis.
+Cairo, Tel Aviv, and Los Angeles were the top three trending just over 3000 annual sunshine hours while Brussels, Dublin, and Taipei were the bottom three with around 1500 annual sunshine hours."}
+top_10 <- healthy_data %>% 
+  arrange(desc(`Sunshine hours(City)`)) %>% 
+  slice(1:10) %>% 
+  ggplot(aes(y = fct_reorder(City,`Sunshine hours(City)`), x = `Sunshine hours(City)`)) +
+  geom_col(fill = "khaki") +
+  labs(title = "Top 10 and Bottom 10 Cities by Annual Sunshine Hours",
+       y = "",
+       x = "") +
+  dark_theme_minimal()
+
+bottom_10 <- healthy_data %>% 
+  arrange(`Sunshine hours(City)`) %>% 
+  slice(1:10) %>% 
+  ggplot(aes(y = fct_reorder(City,`Sunshine hours(City)`), x = `Sunshine hours(City)`)) +
+  geom_col(fill = "khaki") +
+  xlim(0,3540) +
+  labs(y = "",
+       x = "",
+       caption = "Data from UK Healthy Lifestyle Cities Report 2021, Graph by Jocelyn Radke") +
+  dark_theme_minimal()
+
+grid.arrange(top_10, bottom_10, nrow=2)
+```

### 2022-04-19 initialdraft.Rmd
cat graph

--- 2022-04-19 initialdraft.Rmd
@@
 library(tidyverse)
+library(lubridate) 
+library(ggthemes)
 ```
@@
 ```
+
+```{r, r.height = 20, r.width = 15, fig.alt= "This dot plot compares the level of happiness to the sunshine hours in 43 different locations from the Healthy Lifestyle Cities Report 2021.
+The dots are all assigned a color based on location, and plotted at each discrete point.
+There appears to be no strong correlation between isolating the sunshine hours and comparing them to the happiness level.
+More factors combine to make up overall happiness."}
+healthy_lifestyle_data_cat <- healthy_data_dollars[-c(20),]
+
+healthy_lifestyle_data_cat %>% 
+  select(`City`, `Happiness levels(Country)`, `Sunshine hours(City)`) %>%
+
+  ggplot(aes(x = `Happiness levels(Country)`, 
+             y = factor(`Sunshine hours(City)`), 
+             color = (`City`))) +
+  geom_count() +
+  scale_y_discrete(breaks = c(1405, 1884, 2363, 2983, 3542))+
+
+  labs(title = "Is there a correlation between sunshine hours and happiness levels?",
+       x = "Happiness Level",
+       y = "Sunshine Hours",
+       caption = "Graph By Cat Terres; data sourced from Kaggle, 
+       'Healthy Lifestyle Cities Report 2021'") +
+
+  theme_foundation() +
+  theme(legend.title=element_blank())+
+  theme(legend.background = element_blank())
+
+```

### 2022-04-19 initialdraft.Rmd
updated libraries
ana commit

@@
 ```
+```{r, fig.alt= "Scatterplot showing the relationship between the precentage of Obesity in each city's respective country and the number of take out places in that city." }
+healthy_lifestyle_city_2021 %>% 
+  head(n =10) %>% 
+  select(City, `Obesity levels(Country)`, `Number of take out places(City)`) %>% 
+  ggplot(aes(x = `Obesity levels(Country)`, y = `Number of take out places(City)`, color = City))+
+  geom_point(aes(color = City), size = 3)+
+  labs(title= "Obesity Percentage Variation with Increasing Number of Take Out Places", x = "Country-wide Obesity Levels", y = "Number of Take Out Places in Each City")+
+  scale_color_brewer(palette="Paired"
+                     )+
+  theme(
+  panel.background = element_rect(fill = "steelblue4",
+                                colour = "steelblue4",
+                                size = 0.5,
+                                ),
+  panel.border = element_blank())
+
+```

### 2022-04-19 initialdraft.Rmd
commit

--- 2022-04-19 initialdraft.Rmd
@@
 library(ggthemes)
+library(ggdark)
 ```
@@
 ```
+
+Which cities are the sunniest and least sunny?
+```{r, fig.alt = "Graph of the top 10 and bottom 10 cities by annual sunshine hours.The cities are mapped on the y-axis while the sunshine hours is mapped on the x-axis.
+Cairo, Tel Aviv, and Los Angeles were the top three trending just over 3000 annual sunshine hours while Brussels, Dublin, and Taipei were the bottom three with around 1500 annual sunshine hours."}
+top_10 <- healthy_data_dollars %>% 
+  arrange(desc(`Sunshine hours(City)`)) %>% 
+  slice(1:10) %>% 
+  ggplot(aes(y = fct_reorder(City,`Sunshine hours(City)`), x = `Sunshine hours(City)`)) +
+  geom_col(fill = "khaki") +
+  labs(title = "Top 10 and Bottom 10 Cities by Annual Sunshine Hours",
+       y = "",
+       x = "") +
+  dark_theme_minimal()
+
+bottom_10 <- healthy_data_dollars %>% 
+  arrange(`Sunshine hours(City)`) %>% 
+  slice(1:10) %>% 
+  ggplot(aes(y = fct_reorder(City,`Sunshine hours(City)`), x = `Sunshine hours(City)`)) +
+  geom_col(fill = "khaki") +
+  xlim(0,3540) +
+  labs(y = "",
+       x = "",
+       caption = "Data from UK Healthy Lifestyle Cities Report 2021, Graph by Jocelyn Radke") +
+  dark_theme_minimal()
+
+grid.arrange(top_10, bottom_10, nrow=2)
+```

### 2022-04-19 initialdraft.Rmd
useless commmit yay

--- 2022-04-19 initialdraft.Rmd
@@
 
+Cat's graph:
 ```{r, r.height = 20, r.width = 15, fig.alt= "This dot plot compares the level of happiness to the sunshine hours in 43 different locations from the Healthy Lifestyle Cities Report 2021.
@@
 
-Which cities are the sunniest and least sunny?
+Joce's graph Which cities are the sunniest and least sunny?
 ```{r, fig.alt = "Graph of the top 10 and bottom 10 cities by annual sunshine hours.The cities are mapped on the y-axis while the sunshine hours is mapped on the x-axis.
@@
 ```
+
+Ana's graph
+```{r, fig.alt= "Scatterplot showing the relationship between the precentage of Obesity in each city's respective country and the number of take out places in that city." }
+healthy_lifestyle_city_2021 %>% 
+  head(n =10) %>% 
+  select(City, `Obesity levels(Country)`, `Number of take out places(City)`) %>% 
+  ggplot(aes(x = `Obesity levels(Country)`, y = `Number of take out places(City)`, color = City))+
+  geom_point(aes(color = City), size = 3)+
+  labs(title= "Obesity Percentage Variation with Increasing Number of Take Out Places", x = "Country-wide Obesity Levels", y = "Number of Take Out Places in Each City")+
+  scale_color_brewer(palette="Paired"
+                     )+
+  theme(
+  panel.background = element_rect(fill = "steelblue4",
+                                colour = "steelblue4",
+                                size = 0.5,
+                                ),
+  panel.border = element_blank())
+
+```

### 2022-04-19 initialdraft.Rmd

--- 2022-04-19 initialdraft.Rmd
@@
 ```
+
 ```{r, fig.alt= "Scatterplot showing the relationship between the precentage of Obesity in each city's respective country and the number of take out places in that city." }
-healthy_lifestyle_city_2021 %>% 
+healthy_data %>% 
   head(n =10) %>% 

### 2022-04-19 initialdraft.Rmd

@@
 library(ggthemes)
+library(plotly)
 ```
@@
 
-healthy_lifestyle_data_cat %>% 
+healthy_lifestyle_data_cat2 <- healthy_lifestyle_data_cat %>% 
   select(`City`, `Happiness levels(Country)`, `Sunshine hours(City)`) %>%
@@
 
-Which cities are the sunniest and least sunny?
+plotly for cities
+```{r}
+ggplotly(healthy_lifestyle_data_cat2,
+         tooltip = c("text", 
+                     "x",
+                     "(City)"))
+```
+
+Joce's graph Which cities are the sunniest and least sunny?
 ```{r, fig.alt = "Graph of the top 10 and bottom 10 cities by annual sunshine hours.The cities are mapped on the y-axis while the sunshine hours is mapped on the x-axis.
@@
 
+Ana's graph
+
 ```{r, fig.alt= "Scatterplot showing the relationship between the precentage of Obesity in each city's respective country and the number of take out places in that city." }

### 2022-04-21 initialdraft.Rmd
GDP data is added

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
+#knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
 ```
@@
 library(plotly)
+library(ggdark)
 ```
@@
          gym_cost = `Cost of a monthly gym membership(City)`*1.3)
+```
+
+> Because economic performance is a common standard for measuring the success of a given country, we chose to investigate if there is a correlation between gross domestic product (GDP), which is a measure of the total volume of goods and services produced within in country in a given year, and happiness levels as calculated by the **survey**.
+We used population data to calculate GDP per capita (thereafter, GDPPC) so as to control for differences in population between countries.
+We believe that GDPPC provides a helpful, though imperfect measure of the standard of living within a country.
+GDPPC operates with the assumption that every individual within a country gets an equal slice of the GDP pie, which is unrealistic, however, this is an assumption we will make for the purpose of this analysis.
+We see that countries with higher GDPPC tend to correlate with higher happiness levels than countries with lower GDPPC.
+We wondered if countries with a higher GDPPC would be more unhappy reflecting that they may work longer hours in order to have such a high level of production.
+It is possible that rather than hours worked, GDP reflects differences in technology, production processes, management, or human capital.
+
+```{r}
+country_GDP <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQL_6se7aBLQSP92RgP5DkvQ_quTyzsTxskf9ZFpvE_5ifMS5whQ1Lr0JRNMtd1ZGAaVXlEEMECPMHr/pub?output=csv", 
+    col_types = cols(GDPM = col_number(), 
+        GDP = col_number(), pop = col_number(), 
+        GDPPC = col_number()))
+
+healthy_data_2 <- healthy_data_dollars %>% 
+  left_join(country_GDP,
+            by = c("City" = "city"))
+
+options(scipen=999)
+
+ggplot(healthy_data_2, aes(y = fct_reorder(country, GDPPC), x = GDPPC, color = `Happiness levels(Country)`)) +
+  geom_point() +
+  labs(title = "Gross Domestic Product per Capita by Country and Happiness Level",
+       caption = "Data from: ADD LATER",
+       x = "GDP per capita (USD)",
+       y = "",
+       color = "Happiness Level 
+       (1-10 scale)") +
+  theme(plot.title = element_text(hjust = 1)) +
+  theme_classic() 
+```
+
+#Starting to mess with hours worked but realized that missing data is going to be a problem
+```{r}
+ggplot(healthy_data_2, aes(y = fct_reorder(City, `Annual avg. hours worked`), x = `Annual avg. hours worked`, color = `Happiness levels(Country)`)) +
+  geom_point() +
+  labs(title = "",
+       caption = "Data from: ADD LATER",
+       x = "",
+       y = "",
+       color = "Happiness Level 
+       (1-10 scale)") +
+  theme(plot.title = element_text(hjust = 1)) +
+  theme_classic() 
 ```

### 2022-04-21 initialdraft.Rmd
added GDP source link
added hours worked data

@@
 
+[GDP data source](https://worldpopulationreview.com/countries/countries-by-gdp)
+
 ```{r}
@@
 ```{r}
-ggplot(healthy_data_2, aes(y = fct_reorder(City, `Annual avg. hours worked`), x = `Annual avg. hours worked`, color = `Happiness levels(Country)`)) +
+ggplot(healthy_data_2, aes(y = fct_reorder(City, `Hours Worked`), x = `Hours Worked`, color = `Happiness levels(Country)`)) +
   geom_point() +

### 2022-04-21 initialdraft.Rmd
Cat's graphs pasted in

@@
 
-Cat's graph:
+Cat's graph(s):
+
+We chose three variables that we think are important contributing factors to overall happiness, influenced of course by where we are and salient factors we feel attuned to.
+Our variables, life expectancy, sunshine hours, and hours worked, are compared against overall happiness for each place to see if there is a correlation between more or less of each variable.
+We are also keeping in mind intangible factors such as state of mind and the impacts of cultural attitudes.
+
 ```{r, r.height = 20, r.width = 15, fig.alt= "This dot plot compares the level of happiness to the sunshine hours in 43 different locations from the Healthy Lifestyle Cities Report 2021.
@@
                      "(City)"))
+```
+
+Life expectancy vs. Happiness (factor in city)
+Does happiness affect life expectancy?
+
+```{r, fig.alt= "For this graph, the cities have been placed into bins based on the happiness level and the range they fall into.
+For example, a country with a happiness level of 4.5 would be placed within the box plot above the "4-5" on the x axis.
+They are then plotted using upper and lower quartiles to show the distribution of life expectancies."}
+bin_size <- 1
+healthy_data_dollars %>% 
+  select("City" = `City`, "Happiness Level" = `Happiness levels(Country)`, "Life Expectancy" = `Life expectancy(years) (Country)`) %>% 
+  arrange(desc(`Life Expectancy`)) %>%
+
+  mutate(bin_dist = paste(as.character(as.integer(`Happiness Level`)),as.character(as.integer(`Happiness Level`+1)), sep = "-")) %>%  
+  ggplot() +
+  geom_boxplot(aes(x = factor(bin_dist), 
+         y = `Life Expectancy`,
+         outlier.color = NULL,
+         fill = bin_dist
+         )) +
+  labs(title = "Does reported greater happiness have a positive effect on life expectancy?",
+       x = "Happiness Level",
+       y = "Life Expectancy",
+       fill = "") +
+
+  guides(y = guide_axis(angle = 45))
+
+```
+
+Hours Worked vs. Happiness (factor in city)
+Is there a correlation between happiness and hours worked?
+#This one is still a work in progress
+```{r}
+##waiting on revised hours worked data
+healthy_data_dollars %>% 
+  select(`City`, "Happiness Level" = `Happiness levels(Country)`, "Average Annual Hours Worked" = `Annual avg. hours worked`) %>% 
+  arrange(desc(`Average Annual Hours Worked`)) %>%
+
+  mutate(bin_dist = paste(as.character(as.integer(`Happiness Level`)),as.character(as.integer(`Happiness Level`+1)), sep = "-")) %>%
+
+  ggplot(aes(x = factor(bin_dist),
+             y = `Average Annual Hours Worked`
+             )) +
+  geom_col()
+
 ```

### 2022-04-21 initialdraft.Rmd
Added my Obesity and Life Expec. Graph

@@
 ```
+
+```{r, fig.alt= Interactive plot showing the relationship between life expectancy in years and the obesity percentage of each city's respective country}
+obesity_life <-
+healthy_data_dollars %>% 
+  select(`City`, `Life expectancy(years) (Country)`, `Obesity levels(Country)`) %>% 
+  arrange(`Obesity levels(Country)`) %>% 
+  ggplot(aes(x = `Obesity levels(Country)`, y = `Life expectancy(years) (Country)`, color = `City`))+
+  geom_point()+
+  labs(title = "Life Expectancy by Country and its Relationship to Obesity Levels ")+
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "lightblue",
+                                colour = "gray",
+                                size = 0.5,
+                                ))
+
+  ggplotly(obesity_life,
+         tooltip = c("text", 
+                     "x",
+                     "City"))
+
+```
+
+>From the graph, we can appreciate a few patterns: There is a slight grouping of cities towards the lower Obesity levels (<10%), that relates to a mid-to-high Life Expectancy.
+Another cluster is observable in the 20-30% obesity range, with a majority of those cities showing a high life expectancy.
+It is interesting to note that most of these cities are European, as opposed to other cities at a similar Obesity level, which show lower Life Expectancy and are in the American continent.
+Finally, we can also observe a last group in the (>30%) Obesity levels, which show a small variation in Life Expectancy, with Washington DC showing the highest Life Expectacy in the group.

### 2022-04-22 initialdraft.Rmd
jocelyn 9:49pm

--- 2022-04-21 initialdraft.Rmd
@@
 #Starting to mess with hours worked but realized that missing data is going to be a problem
+[new hours worked data (Penn)](https://worldpopulationreview.com/country-rankings/average-work-week-by-country)
 ```{r}

### 2022-04-26 initialdraft.Rmd
jocelyn 9:50pm
new draft

--- 2022-04-21 initialdraft.Rmd
@@
 ---
-title: 'finalproj'
-author: "Jocelyn, Ana, Cat"
+title: 'Final Project Draft (enter actual title later)'
+author: "Jocelyn Radke, Ana Espeleta, Cat Terres"
 output: 
@@
 ```{r setup, include=FALSE}
-#knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
+knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
 ```
@@
 ```{r}
+#Loading the packages
 library(dplyr)
@@
 
+## Introduction and Background
+
+- Research question: Does money buy happiness?
+- Challenging the assumption that the best countries are those that are most economically successful by looking at indicators of well-being instead of just GDP/output/wealth
+- Does the amount of sunshine correlate with "happier" people?
+- Is there a correlation between life expectancy and happiness?
+
+## Data Collection
+- Healthy living report (main source)- [Healthy Lifestyle Cities Report 2021](https://www.kaggle.com/datasets/prasertk/healthy-lifestyle-cities-report-2021)
+- GDP info (supplementary source)- [GDP data source](https://worldpopulationreview.com/countries/countries-by-gdp)
+- Hours worked info (supplementary source)- [new hours worked data (Penn)](https://worldpopulationreview.com/country-rankings/average-work-week-by-country)
+
+## Analysis
+
 ```{r}
+#Loading the data
 healthy_data <- read_csv("healthy_lifestyle_city_2021.csv", 
@@
 
-# converting to dollars
+#Converting to dollars
 healthy_data_dollars <- healthy_data %>% 
@@
 It is possible that rather than hours worked, GDP reflects differences in technology, production processes, management, or human capital.
-
-[GDP data source](https://worldpopulationreview.com/countries/countries-by-gdp)
 
@@
 
-#Starting to mess with hours worked but realized that missing data is going to be a problem
+#Happiness level by hours worked
 ```{r}
@@
 
-We chose three variables that we think are important contributing factors to overall happiness, influenced of course by where we are and salient factors we feel attuned to.
+> We chose three variables that we think are important contributing factors to overall happiness, influenced of course by where we are and salient factors we feel attuned to.
 Our variables, life expectancy, sunshine hours, and hours worked, are compared against overall happiness for each place to see if there is a correlation between more or less of each variable.
@@
 ```{r, fig.alt= "For this graph, the cities have been placed into bins based on the happiness level and the range they fall into.
-For example, a country with a happiness level of 4.5 would be placed within the box plot above the "4-5" on the x axis.
+For example, a country with a happiness level of 4.5 would be placed within the box plot above the 4-5 on the x axis.
 They are then plotted using upper and lower quartiles to show the distribution of life expectancies."}
@@
 
-Joce's graph Which cities are the sunniest and least sunny?
+Joce's graph- Which cities are the sunniest and least sunny?
 ```{r, fig.alt = "Graph of the top 10 and bottom 10 cities by annual sunshine hours.The cities are mapped on the y-axis while the sunshine hours is mapped on the x-axis.
@@
 Ana's graph
+- maybe make this one a plotly?
 
@@
 
-```{r, fig.alt= Interactive plot showing the relationship between life expectancy in years and the obesity percentage of each city's respective country}
+```{r, fig.alt= "Interactive plot showing the relationship between life expectancy in years and the obesity percentage of each city's respective country"}
 obesity_life <-
@@
 
->From the graph, we can appreciate a few patterns: There is a slight grouping of cities towards the lower Obesity levels (<10%), that relates to a mid-to-high Life Expectancy.
+> From the graph, we can appreciate a few patterns: There is a slight grouping of cities towards the lower Obesity levels (<10%), that relates to a mid-to-high Life Expectancy.
 Another cluster is observable in the 20-30% obesity range, with a majority of those cities showing a high life expectancy.

### 2022-04-26 draft2.Rmd
original commit

--- 2022-04-26 initialdraft.Rmd
@@
 ---
-title: 'Final Project Draft (enter actual title later)'
+title: 'Final Project Draft #2'
 author: "Jocelyn Radke, Ana Espeleta, Cat Terres"
@@
   theme(legend.background = element_blank())
-
 ```

### 2022-04-26 draft2.Rmd
commit!

@@
 ```
-
-Joce's graph- Which cities are the sunniest and least sunny?
-```{r, fig.alt = "Graph of the top 10 and bottom 10 cities by annual sunshine hours.The cities are mapped on the y-axis while the sunshine hours is mapped on the x-axis.
-Cairo, Tel Aviv, and Los Angeles were the top three trending just over 3000 annual sunshine hours while Brussels, Dublin, and Taipei were the bottom three with around 1500 annual sunshine hours."}
-top_10 <- healthy_data %>% 
-  arrange(desc(`Sunshine hours(City)`)) %>% 
-  slice(1:10) %>% 
-  ggplot(aes(y = fct_reorder(City,`Sunshine hours(City)`), x = `Sunshine hours(City)`)) +
-  geom_col(fill = "khaki") +
-  labs(title = "Top 10 and Bottom 10 Cities by Annual Sunshine Hours",
-       y = "",
-       x = "") +
-  dark_theme_minimal()
-
-bottom_10 <- healthy_data %>% 
-  arrange(`Sunshine hours(City)`) %>% 
-  slice(1:10) %>% 
-  ggplot(aes(y = fct_reorder(City,`Sunshine hours(City)`), x = `Sunshine hours(City)`)) +
-  geom_col(fill = "khaki") +
-  xlim(0,3540) +
-  labs(y = "",
-       x = "",
-       caption = "Data from UK Healthy Lifestyle Cities Report 2021, Graph by Jocelyn Radke") +
-  dark_theme_minimal()
-
-grid.arrange(top_10, bottom_10, nrow=2)
-```
-
-Ana's graph
-- maybe make this one a plotly?
-
-```{r, fig.alt= "Scatterplot showing the relationship between the precentage of Obesity in each city's respective country and the number of take out places in that city." }
-healthy_data %>% 
-  head(n =10) %>% 
-  select(City, `Obesity levels(Country)`, `Number of take out places(City)`) %>% 
-  ggplot(aes(x = `Obesity levels(Country)`, y = `Number of take out places(City)`, color = City))+
-  geom_point(aes(color = City), size = 3)+
-  labs(title= "Obesity Percentage Variation with Increasing Number of Take Out Places", x = "Country-wide Obesity Levels", y = "Number of Take Out Places in Each City")+
-  scale_color_brewer(palette="Paired"
-                     )+
-  theme(
-  panel.background = element_rect(fill = "steelblue4",
-                                colour = "steelblue4",
-                                size = 0.5,
-                                ),
-  panel.border = element_blank())
-
-```
-
-```{r, fig.alt= "Interactive plot showing the relationship between life expectancy in years and the obesity percentage of each city's respective country"}
-obesity_life <-
-healthy_data_dollars %>% 
-  select(`City`, `Life expectancy(years) (Country)`, `Obesity levels(Country)`) %>% 
-  arrange(`Obesity levels(Country)`) %>% 
-  ggplot(aes(x = `Obesity levels(Country)`, y = `Life expectancy(years) (Country)`, color = `City`))+
-  geom_point()+
-  labs(title = "Life Expectancy by Country and its Relationship to Obesity Levels ")+
-  theme(legend.position = "none",
-        panel.background = element_rect(fill = "lightblue",
-                                colour = "gray",
-                                size = 0.5,
-                                ))
-
-  ggplotly(obesity_life,
-         tooltip = c("text", 
-                     "x",
-                     "City"))
-
-```
-
-> From the graph, we can appreciate a few patterns: There is a slight grouping of cities towards the lower Obesity levels (<10%), that relates to a mid-to-high Life Expectancy.
-Another cluster is observable in the 20-30% obesity range, with a majority of those cities showing a high life expectancy.
-It is interesting to note that most of these cities are European, as opposed to other cities at a similar Obesity level, which show lower Life Expectancy and are in the American continent.
-Finally, we can also observe a last group in the (>30%) Obesity levels, which show a small variation in Life Expectancy, with Washington DC showing the highest Life Expectacy in the group.

### 2022-04-26 draft2.Rmd
commit #3

@@
 library(ggdark)
+library(maps)
+library(ggmap)
 ```
@@
 ```{r}
-country_GDP <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQL_6se7aBLQSP92RgP5DkvQ_quTyzsTxskf9ZFpvE_5ifMS5whQ1Lr0JRNMtd1ZGAaVXlEEMECPMHr/pub?output=csv", 
+supplemental_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQL_6se7aBLQSP92RgP5DkvQ_quTyzsTxskf9ZFpvE_5ifMS5whQ1Lr0JRNMtd1ZGAaVXlEEMECPMHr/pub?output=csv", 
     col_types = cols(GDPM = col_number(), 
@@
 healthy_data_2 <- healthy_data_dollars %>% 
-  left_join(country_GDP,
+  left_join(supplemental_data,
             by = c("City" = "city"))
@@
 
-#Happiness level by hours worked
 ```{r}
-ggplot(healthy_data_2, aes(y = fct_reorder(City, `Hours Worked`), x = `Hours Worked`, color = `Happiness levels(Country)`)) +
-  geom_point() +
-  labs(title = "",
-       caption = "Data from: ADD LATER",
-       x = "",
-       y = "",
-       color = "Happiness Level 
-       (1-10 scale)") +
-  theme(plot.title = element_text(hjust = 1)) +
-  theme_classic() 
+healthy_data_2 %>% 
+  filter(country == "Canada")
+
+# Get the map information
+world <- get_stamenmap(
+    bbox = c(left = -180, bottom = -57, right = 179, top = 82.1), 
+    maptype = "terrain",
+    zoom = 2)
+
+# Plot the points on the map
+ggmap(world) + # creates the map "background"
+  geom_point(data = healthy_data_2 %>% 
+  filter(country == "Canada"), 
+             aes(x = Longitude, y = Latitude), 
+             size = 0.5, color = "red") +
+  theme_map()
 ```

### 2022-04-26 draft2.Rmd
Cat Graph

@@
 Is there a correlation between happiness and hours worked?
-#This one is still a work in progress
+
 ```{r}
-##waiting on revised hours worked data
-healthy_data_dollars %>% 
-  select(`City`, "Happiness Level" = `Happiness levels(Country)`, "Average Annual Hours Worked" = `Annual avg. hours worked`) %>% 
-  arrange(desc(`Average Annual Hours Worked`)) %>%
+healthy_data_dot <- healthy_data_2 [-c(23),]
 
-  mutate(bin_dist = paste(as.character(as.integer(`Happiness Level`)),as.character(as.integer(`Happiness Level`+1)), sep = "-")) %>%
+Healthy <- healthy_data_dot %>% 
+  select(`City`, "Happiness Level" = `Happiness levels(Country)`, "Average Weekly Hours Worked" = `Hours Worked`) %>% 
+  mutate(`Avg. Weekly Hours Worked` = factor(`Average Weekly Hours Worked`)) %>%
 
-  ggplot(aes(x = factor(bin_dist),
-             y = `Average Annual Hours Worked`
-             )) +
-  geom_col()
+  #mutate(bin_dist = paste(as.character(as.integer(`Happiness Level`)),as.character(as.integer(`Happiness Level`+1)), sep = "-")) %>%
+
+ ggplot(aes(x = `Happiness Level`, 
+             y = `Avg. Weekly Hours Worked`, 
+             color = `City`)) +
+  geom_point() +
+  scale_y_discrete(breaks = c(26.6, 30.6, 33.2, 38.8, 42.1))+
+
+  labs(title = "Is there a correlation between weekly work hours and happiness levels?",
+       x = "Happiness Level",
+       y = "",
+       caption = "Graph By Cat Terres; data sourced from Kaggle, 
+       'Healthy Lifestyle Cities Report 2021'",
+       color = "") +
+
+  theme_foundation() +
+  theme(legend.title=element_blank())+
+  theme(legend.background = element_blank())
 
 ```
+
+```{r}
+ggplotly(Healthy,
+         tooltip = c("text",
+                     "y",
+                     "x",
+                     "City"))
+```

### 2022-04-26 draft2.Rmd
joce adding map

@@
 ```{r}
-healthy_data_2 %>% 
-  filter(country == "Canada")
-
 # Get the map information
@@
     bbox = c(left = -180, bottom = -57, right = 179, top = 82.1), 
-    maptype = "terrain",
+    maptype = "toner-lite",
     zoom = 2)
@@
 # Plot the points on the map
-ggmap(world) + # creates the map "background"
-  geom_point(data = healthy_data_2 %>% 
-  filter(country == "Canada"), 
+map <- ggmap(world) + # creates the map "background"
+  geom_point(data = healthy_data_2, 
              aes(x = Longitude, y = Latitude), 
@@
   theme_map()
+
+ggplotly(map,
+         tooltip = c("text", "City"))
 ```

### 2022-04-26 draft2.Rmd
Cat Alt Text

--- 2022-04-26 draft2.Rmd
@@
 
-```{r}
+```{r, fig.alt= "This graph displays various cities with their own color coded dot based on happiness level (x axis) and weekly hours worked (y axis).
+There is a loose correlation between greater happiness and fewer weeky work hours.
+The dots are able to be scrolled over with the cursor, displaying exact happiness level, exact work hours, and city."}
 healthy_data_dot <- healthy_data_2 [-c(23),]

### 2022-04-26 draft2.Rmd
Added GDPC vs. Hours Worked Graph

@@
 ```
+
+#GDPPC vs.
+Hours Worked (Can we observe a relationship between the GDPC of each contry and the average amount of hours people work per week?) Can the observable patterns tell us something about the contries with low GDPC and a higher number of working hours?
+How can we relate this to happiness?
+
+```{r}
+country_GDP <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQL_6se7aBLQSP92RgP5DkvQ_quTyzsTxskf9ZFpvE_5ifMS5whQ1Lr0JRNMtd1ZGAaVXlEEMECPMHr/pub?output=csv", 
+    col_types = cols(GDPM = col_number(), 
+        GDP = col_number(), pop = col_number(), 
+        GDPPC = col_number()))
+
+healthy_data_2 <- healthy_data_dollars %>% 
+  left_join(country_GDP,
+            by = c("City" = "city"))
+
+options(scipen=999)
+
+GDPP_hours <- healthy_data_2 %>% 
+ggplot( aes(y = GDPPC, x = `Hours Worked`, color = `City`)) +
+  geom_point() +
+  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
+       caption = "Data from: ADD LATER",
+       y = "GDP per capita (USD)",
+       x = "Hours Worked (Weekly)",
+       color = "") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "lightblue",
+                                colour = "gray",
+                                size = 0.5,
+                                ),
+        plot.title = element_text(size = 0.05))
+
+ggplotly(GDPP_hours,
+         tooltip = c("text", 
+                     "x",
+                     "City"))
+```

### 2022-04-27 draft2.Rmd
switched the axis

@@
 GDPP_hours <- healthy_data_2 %>% 
-ggplot( aes(y = GDPPC, x = `Hours Worked`, color = `City`)) +
+ggplot( aes(x = GDPPC, y = `Hours Worked`, color = `City`)) +
   geom_point() +
@@
        caption = "Data from: ADD LATER",
-       y = "GDP per capita (USD)",
-       x = "Hours Worked (Weekly)",
+       x = "GDP per capita (USD)",
+       y = "Hours Worked (Weekly)",
        color = "") +

### 2022-04-28 draft2.Rmd
finished intro! yay!

@@
 ---
-title: 'Final Project Draft #2'
+title: 'Can money buy happiness?'
 author: "Jocelyn Radke, Ana Espeleta, Cat Terres"
@@
 
-- Research question: Does money buy happiness?
-- Challenging the assumption that the best countries are those that are most economically successful by looking at indicators of well-being instead of just GDP/output/wealth
-- Does the amount of sunshine correlate with "happier" people?
-- Is there a correlation between life expectancy and happiness?
+Can money buy happiness?
+Philosophers, university students, and lay people alike have grappled with this question for ages.
+The knee-jerk reaction is to emphatically reject a link between life satisfaction and financial abundance because everyone knows both miserable wealthy people and others who appear incredibly joyful despite severe financial difficulties.
+As one rapper (The Notorious B.I.G.) insightfully observed that, “Mo Money Mo Problems,” which illustrates that affluence prompts challenges of its own.
+Some researchers have turned to empirical testing to seek an answer to this question.
+One study by [Jachimowicz](https://www.hbs.edu/ris/Publication%20Files/FinancialScarcity_SPPS_accepted_November1_2021_06f87dd3-4474-4c92-88d1-a5c6b63a2eaa.pdf) and colleagues found that financial instability correlates with higher levels of daily distress.
+Although money alone doesn’t imply happiness, money can eliminate daily hardships that lead to life dissatisfaction.
+A 2010 [Princeton](https://spia.princeton.edu/sites/default/files/content/docs/news/Happiness_Money_Summary.pdf) study measured that a $75,000 annual income was the “sweet spot” for maximizing emotional well-being.
+Incomes below this benchmark were correlated with lower levels of happiness and higher levels of stress.
+These research studies and our own analysis seek to make a connection between standards of living (a quantitative measure) and quality of life (a qualitative measure).
+A standard of living measures the material well-being of people in a given geographical population which is reflected in factors such as comfort, access to opportunities, goods, healthcare services, and safety.
+Quality of life, on the other hand, is a more subjective term that reflects the level of happiness of a population, which certainly varies person to person.
+
+> “Wealth consists not in having great possessions, but in having few wants.” – Epictetus, stoic philosopher
+
+Economic performance is a common determinate of standard of living within a country.
+The reasoning goes that a country that functions well economically is able to provide stable income and access to jobs, increase the availability of goods and services, and afford a social safety net.
+The most common measure of standard of living is gross domestic product (GDP), which is a measure of the total volume of goods and services produced within in country in a given year.
+We paired GDP data with population data to calculate GDP per capita (thereafter, GDPPC) so as to control for differences in population between countries.
+We believe that GDPPC provides a helpful, though imperfect measure of the standard of living within a country.
+GDPPC operates with the assumption that every individual within a country gets an equal slice of the GDP pie, which is unrealistic because of widespread income inequality, however, can provide insight as long as we are mindful of its limitations.
+In what follows, we seek to challenge the assumption that the best countries are those that are most economically successful though looking at measures of quality of living in addition to standard of living.
 

### 2022-04-28 draft2.Rmd
added map! - Joce

@@
 library(ggmap)
+library(leaflet)
+library(RColorBrewer)
 ```
@@
 
-#Converting to dollars
-healthy_data_dollars <- healthy_data %>% 
+supplemental_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQL_6se7aBLQSP92RgP5DkvQ_quTyzsTxskf9ZFpvE_5ifMS5whQ1Lr0JRNMtd1ZGAaVXlEEMECPMHr/pub?output=csv", 
+    col_types = cols(GDPM = col_number(), 
+        GDP = col_number(), pop = col_number(), 
+        GDPPC = col_number()))
+
+#Joining data and converting pounds to dollars
+healthy_data_2 <- healthy_data %>% 
+  left_join(supplemental_data,
+            by = c("City" = "city")) %>% 
   mutate(water_bottle_cost = `Cost of a bottle of water(City)`*1.3,
@@
 ```
+Here is a map of the cities included in the analysis. European cities are likely overrepresented because the data was compiled by a UK-based company.  
+```{r}
+labels <- sprintf(
+  "<strong>%s</strong><br/> %s",
+  healthy_data_2$City, healthy_data_2$country) %>%
+  lapply(htmltools::HTML)
+
+leaflet(data = healthy_data_2) %>% 
+  addProviderTiles(providers$CartoDB.Positron) %>%
+  addCircleMarkers(
+    radius = 4,
+    color = "#D4A200",
+    stroke = FALSE, 
+    fillOpacity = 0.7,
+    label = ~labels
+  )
+```
 
 > Because economic performance is a common standard for measuring the success of a given country, we chose to investigate if there is a correlation between gross domestic product (GDP), which is a measure of the total volume of goods and services produced within in country in a given year, and happiness levels as calculated by the **survey**.
-We used population data to calculate GDP per capita (thereafter, GDPPC) so as to control for differences in population between countries.
-We believe that GDPPC provides a helpful, though imperfect measure of the standard of living within a country.
-GDPPC operates with the assumption that every individual within a country gets an equal slice of the GDP pie, which is unrealistic, however, this is an assumption we will make for the purpose of this analysis.
 We see that countries with higher GDPPC tend to correlate with higher happiness levels than countries with lower GDPPC.
@@
 ```{r}
-supplemental_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQL_6se7aBLQSP92RgP5DkvQ_quTyzsTxskf9ZFpvE_5ifMS5whQ1Lr0JRNMtd1ZGAaVXlEEMECPMHr/pub?output=csv", 
-    col_types = cols(GDPM = col_number(), 
-        GDP = col_number(), pop = col_number(), 
-        GDPPC = col_number()))
-
-healthy_data_2 <- healthy_data_dollars %>% 
-  left_join(supplemental_data,
-            by = c("City" = "city"))
-
 options(scipen=999)
@@
   theme(plot.title = element_text(hjust = 1)) +
-  theme_classic() 
-```
-
-```{r}
-# Get the map information
-world <- get_stamenmap(
-    bbox = c(left = -180, bottom = -57, right = 179, top = 82.1), 
-    maptype = "toner-lite",
-    zoom = 2)
-
-# Plot the points on the map
-map <- ggmap(world) + # creates the map "background"
-  geom_point(data = healthy_data_2, 
-             aes(x = Longitude, y = Latitude), 
-             size = 0.5, color = "red") +
-  theme_map()
-
-ggplotly(map,
-         tooltip = c("text", "City"))
+  theme_classic() +
+  scale_color_gradient(high = "#FFD25A", low = "black")
 ```

### 2022-04-28 draft2.Rmd
Cat Graph, Analysis

@@
 
-> We chose three variables that we think are important contributing factors to overall happiness, influenced of course by where we are and salient factors we feel attuned to.
-Our variables, life expectancy, sunshine hours, and hours worked, are compared against overall happiness for each place to see if there is a correlation between more or less of each variable.
-We are also keeping in mind intangible factors such as state of mind and the impacts of cultural attitudes.
+> This graph simply presents reported happiness level against the average weekly hours worked.The data comes from a study on healthy lifestyle elements such as sunshine hours in each place, price of a bottle of water, and ________.
+Our marked interest in working hours out of all the factors in our initial dataset stems from what we witness each and every day in our lives, communities, and the nation at large.
+We wanted to see how hours worked We speculated that fewer weekly work hours would correlate to a greater happiness level, and the graph presents a loose trend that backs our speculations.
+The city with the fewest working hours (Copenhagen) reports a happiness level of 7.64.
+Though this is not the highest happiness level (that would be Helsinki), it is significantly higher than, say, Hong Kong where the work hours are around 41.7, on average paired, with a happiness level of 5.51.
+We recognize that there are cultural, political, and societal factors that could affect this rating.
 
-```{r, r.height = 20, r.width = 15, fig.alt= "This dot plot compares the level of happiness to the sunshine hours in 43 different locations from the Healthy Lifestyle Cities Report 2021.
-The dots are all assigned a color based on location, and plotted at each discrete point.
-There appears to be no strong correlation between isolating the sunshine hours and comparing them to the happiness level.
-More factors combine to make up overall happiness."}
-healthy_lifestyle_data_cat <- healthy_data_dollars[-c(20),]
+```{r}
 
-healthy_lifestyle_data_cat2 <- healthy_lifestyle_data_cat %>% 
-  select(`City`, `Happiness levels(Country)`, `Sunshine hours(City)`) %>%
-
-  ggplot(aes(x = `Happiness levels(Country)`, 
-             y = factor(`Sunshine hours(City)`), 
-             color = (`City`))) +
-  geom_count() +
-  scale_y_discrete(breaks = c(1405, 1884, 2363, 2983, 3542))+
-
-  labs(title = "Is there a correlation between sunshine hours and happiness levels?",
-       x = "Happiness Level",
-       y = "Sunshine Hours",
-       caption = "Graph By Cat Terres; data sourced from Kaggle, 
-       'Healthy Lifestyle Cities Report 2021'") +
-
-  theme_foundation() +
-  theme(legend.title=element_blank())+
-  theme(legend.background = element_blank())
-```
-
-plotly for cities
-```{r}
-ggplotly(healthy_lifestyle_data_cat2,
-         tooltip = c("text", 
-                     "x",
-                     "(City)"))
-```
-
-Life expectancy vs. Happiness (factor in city)
-Does happiness affect life expectancy?
-
-```{r, fig.alt= "For this graph, the cities have been placed into bins based on the happiness level and the range they fall into.
-For example, a country with a happiness level of 4.5 would be placed within the box plot above the 4-5 on the x axis.
-They are then plotted using upper and lower quartiles to show the distribution of life expectancies."}
-bin_size <- 1
-healthy_data_dollars %>% 
-  select("City" = `City`, "Happiness Level" = `Happiness levels(Country)`, "Life Expectancy" = `Life expectancy(years) (Country)`) %>% 
-  arrange(desc(`Life Expectancy`)) %>%
-
-  mutate(bin_dist = paste(as.character(as.integer(`Happiness Level`)),as.character(as.integer(`Happiness Level`+1)), sep = "-")) %>%  
-  ggplot() +
-  geom_boxplot(aes(x = factor(bin_dist), 
-         y = `Life Expectancy`,
-         outlier.color = NULL,
-         fill = bin_dist
-         )) +
-  labs(title = "Does reported greater happiness have a positive effect on life expectancy?",
-       x = "Happiness Level",
-       y = "Life Expectancy",
-       fill = "") +
-
-  guides(y = guide_axis(angle = 45))
-
-```
-
-Hours Worked vs. Happiness (factor in city)
-Is there a correlation between happiness and hours worked?
-
-```{r, fig.alt= "This graph displays various cities with their own color coded dot based on happiness level (x axis) and weekly hours worked (y axis).
-There is a loose correlation between greater happiness and fewer weeky work hours.
-The dots are able to be scrolled over with the cursor, displaying exact happiness level, exact work hours, and city."}
 healthy_data_dot <- healthy_data_2 [-c(23),]
@@
                      "x",
-                     "City"))
+                     "City")) %>% 
+  layout(title = list(text = paste0('Is there a correlation between weekly work hours and happiness levels?',
+                                    '<br>',
+                                    '<sup>',
+                                    'Graph by Cat Terres, data sourced from Kaggle ____ and _____',
+                                    '</sup>')))
 ```
@@
 ```
+
+>Analysis: Can money buy happiness?
+Our key findings from this project are ______________.
+We sought to tell a story about the connection between economic prosperity and happiness but with the added factor of working hours.
+Money is inextricable from the work needed to obtain it, and to base our argument purely on GDP or how much money is possessed completely ignores a key factor: how much are people working to obtain said money.
+Thus, we tied the two together, factoring in that having more money likely ______ and working fewer hours means that people will _____________.
+This presents a paradox of sorts, more work generally means more money, and more money means more happiness, but less work also generates more happiness.
+So where is a harmonious balance found?
+We see that ________.
+Our research cannot possibly cover all factors such as access to community programs, optimal living conditions, or types of government and the length to which they go to provide resources.
+All of these ancillary factors play a role in happiness and the ability to work fewer hours, but we posit that looking purely at money and work can still produce illuminating discoveries.

### 2022-04-28 draft2.Rmd
fixed issue w knitting

@@
 ```
-Here is a map of the cities included in the analysis. European cities are likely overrepresented because the data was compiled by a UK-based company.  
+Here is a map of the cities included in the analysis. European cities are over-represented because the data was compiled by a UK-based company.  
 ```{r}
@@
 ```{r}
-country_GDP <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQL_6se7aBLQSP92RgP5DkvQ_quTyzsTxskf9ZFpvE_5ifMS5whQ1Lr0JRNMtd1ZGAaVXlEEMECPMHr/pub?output=csv", 
-    col_types = cols(GDPM = col_number(), 
-        GDP = col_number(), pop = col_number(), 
-        GDPPC = col_number()))
-
-healthy_data_2 <- healthy_data_dollars %>% 
-  left_join(country_GDP,
-            by = c("City" = "city"))
-
-options(scipen=999)
-
 GDPP_hours <- healthy_data_2 %>% 

### 2022-04-28 draft2.Rmd
commit -jocelyn

@@
 
-> Because economic performance is a common standard for measuring the success of a given country, we chose to investigate if there is a correlation between gross domestic product (GDP), which is a measure of the total volume of goods and services produced within in country in a given year, and happiness levels as calculated by the **survey**.
-We see that countries with higher GDPPC tend to correlate with higher happiness levels than countries with lower GDPPC.
-We wondered if countries with a higher GDPPC would be more unhappy reflecting that they may work longer hours in order to have such a high level of production.
+> We chose to investigate if there is a correlation between GDP per capita and happiness levels by country.
+We speculated that countries with a higher GDPPC might be less happy reflecting longer work hours required to maintain such a high level of production.
+On the other hand, higher levels of GDP mirror higher standards of living and higher material wealth which could translate to life satisfaction.
+Overall, we found that countries with higher GDPPC tend to correlate with higher happiness levels than countries with lower GDPPC.
 It is possible that rather than hours worked, GDP reflects differences in technology, production processes, management, or human capital.

### 2022-04-28 draft2.Rmd
Added analysis of GDP and hours worked

@@
 
+#GDPPC vs. Hours Worked
+```{r}
+GDPP_hours <- healthy_data_2 %>% 
+ggplot( aes(x = GDPPC, y = `Hours Worked`, color = `City`)) +
+  geom_point() +
+  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
+       caption = "Data from: ADD LATER",
+       x = "GDP per capita (USD)",
+       y = "Hours Worked (Weekly)",
+       color = "") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "lightblue",
+                                colour = "gray",
+                                size = 0.5,
+                                ),
+        plot.title = element_text(size = 0.05))
+
+ggplotly(GDPP_hours,
+         tooltip = c("text", 
+                     "x",
+                     "City"))
+```
+
+This initial graph explores the relationship between GDP per capita and the average number of weekly hours worked in each city.
+It allows us to understand what these two factors tell us about the overall well-being of each city later in the study.
+The plot presents a predominantly inverse relationship between GDP per capita and the number of weekly hours worked.
+A cluster of cities is in the range of $0-$20K GDP per capita, and except for one city (Johannesburg), all can be classified as Latin American or Asian.
+We can infer that this relationship may describe different production systems and processes in each country.
+A lower GDP and higher number of hours worked likely points to a lack of access to technological resources or poor organizational management which makes it difficult to increase the standard of living.
+Countries with higher levels of technology can produce the same output as a country with lower levels of technology with much fewer inputs of labor or machinery hours.
+The second observable cluster on this plot is within the bounds of $40K-$60K GDP per capita, with a range of 12.2 between the lowest and highest number of weekly working hours.
+However, most points in the 30-35 weekly working hour range correspond to European cities, which follow the trend of higher GDP per capita and lower working hours.
+In contrast to our previous analyses, the increased GDP may represent more efficiency of labor, which can sustain the economy with fewer working hours and thus, promote a higher standard of living.
+
 > We chose to investigate if there is a correlation between GDP per capita and happiness levels by country.
@@
 
-#GDPPC vs.
-Hours Worked (Can we observe a relationship between the GDPC of each contry and the average amount of hours people work per week?) Can the observable patterns tell us something about the contries with low GDPC and a higher number of working hours?
-How can we relate this to happiness?
-
-```{r}
-GDPP_hours <- healthy_data_2 %>% 
-ggplot( aes(x = GDPPC, y = `Hours Worked`, color = `City`)) +
-  geom_point() +
-  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
-       caption = "Data from: ADD LATER",
-       x = "GDP per capita (USD)",
-       y = "Hours Worked (Weekly)",
-       color = "") +
-  theme(legend.position = "none",
-        panel.background = element_rect(fill = "lightblue",
-                                colour = "gray",
-                                size = 0.5,
-                                ),
-        plot.title = element_text(size = 0.05))
-
-ggplotly(GDPP_hours,
-         tooltip = c("text", 
-                     "x",
-                     "City"))
-```
-
 >Analysis: Can money buy happiness?

### 2022-04-28 draft2.Rmd
commit

--- 2022-04-28 draft2.Rmd
@@
 ```
-Here is a map of the cities included in the analysis. European cities are over-represented because the data was compiled by a UK-based company.  
+Here is a map of the cities included in the analysis. European cities are likely overrepresented because the data was compiled by a UK-based company.  
 ```{r}
@@
 Our marked interest in working hours out of all the factors in our initial dataset stems from what we witness each and every day in our lives, communities, and the nation at large.
-We wanted to see how hours worked We speculated that fewer weekly work hours would correlate to a greater happiness level, and the graph presents a loose trend that backs our speculations.
+We speculated that fewer weekly work hours would correlate to a greater happiness level, and the graph presents a loose trend that backs our speculations.
 The city with the fewest working hours (Copenhagen) reports a happiness level of 7.64.
@@
 ```{r}
+country_GDP <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQL_6se7aBLQSP92RgP5DkvQ_quTyzsTxskf9ZFpvE_5ifMS5whQ1Lr0JRNMtd1ZGAaVXlEEMECPMHr/pub?output=csv", 
+    col_types = cols(GDPM = col_number(), 
+        GDP = col_number(), pop = col_number(), 
+        GDPPC = col_number()))
+
+healthy_data_2 <- healthy_data_dollars %>% 
+  left_join(country_GDP,
+            by = c("City" = "city"))
+
+options(scipen=999)
+
 GDPP_hours <- healthy_data_2 %>% 

### 2022-04-28 draft2.Rmd

--- 2022-04-28 draft2.Rmd
@@
 ```
+
+> Because economic performance is a common standard for measuring the success of a given country, we chose to investigate if there is a correlation between gross domestic product (GDP), which is a measure of the total volume of goods and services produced within in country in a given year, and happiness levels as calculated by the **survey**.
+We see that countries with higher GDPPC tend to correlate with higher happiness levels than countries with lower GDPPC.
+We wondered if countries with a higher GDPPC would be more unhappy reflecting that they may work longer hours in order to have such a high level of production.
+It is possible that rather than hours worked, GDP reflects differences in technology, production processes, management, or human capital.
 
@@
 
-Cat's graph(s):
+> “I think that this is ultimately why we want money: It's to create a world that you prefer." -Hank Green
 
-> This graph simply presents reported happiness level against the average weekly hours worked.The data comes from a study on healthy lifestyle elements such as sunshine hours in each place, price of a bottle of water, and ________.
+> This graph simply presents reported happiness level against the average weekly hours worked.
 Our marked interest in working hours out of all the factors in our initial dataset stems from what we witness each and every day in our lives, communities, and the nation at large.
-We wanted to see how hours worked We speculated that fewer weekly work hours would correlate to a greater happiness level, and the graph presents a loose trend that backs our speculations.
-The city with the fewest working hours (Copenhagen) reports a happiness level of 7.64.
-Though this is not the highest happiness level (that would be Helsinki), it is significantly higher than, say, Hong Kong where the work hours are around 41.7, on average paired, with a happiness level of 5.51.
-We recognize that there are cultural, political, and societal factors that could affect this rating.
+It is easy to assume that those who work less have more time for leisure activities and maintenance of their well-being, and in turn we speculated that fewer weekly work hours would correlate to a greater happiness level.
+However, this graph does not present a strong enough trend to support our hypothesis.
+There is a loose trend, and this can help to give direction to our investigation despite not proving anything for a fact.
+What we DO learn from this graph is the complexity of happiness as a variable.
+Happiness is not only contingent on working hours, but factors such as higher average wages, government investment in citizens and their communities, and access to community resources.
+We recognize that there are cultural, political, and societal nuances that influence whether people work more or less and that different places have different attitudes surrounding work and money.
 
-```{r}
+```{r, fig.width=5, }
 
@@
   mutate(`Avg. Weekly Hours Worked` = factor(`Average Weekly Hours Worked`)) %>%
-
-  #mutate(bin_dist = paste(as.character(as.integer(`Happiness Level`)),as.character(as.integer(`Happiness Level`+1)), sep = "-")) %>%
 
@@
   theme(legend.title=element_blank())+
-  theme(legend.background = element_blank())
+  theme(legend.background = element_blank()) +
+  theme(legend.position = "none")
 
-```
-
-```{r}
 ggplotly(Healthy,
@@
                                     '<sup>',
-                                    'Graph by Cat Terres, data sourced from Kaggle ____ and _____',
+                                    'Graph by Cat Terres, data sourced from Kaggle and World Population Review',
                                     '</sup>')))
+```
+
+#GDPPC vs.
+Hours Worked (Can we observe a relationship between the GDPC of each contry and the average amount of hours people work per week?) Can the observable patterns tell us something about the contries with low GDPC and a higher number of working hours?
+How can we relate this to happiness?
+
+```{r}
+country_GDP <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQL_6se7aBLQSP92RgP5DkvQ_quTyzsTxskf9ZFpvE_5ifMS5whQ1Lr0JRNMtd1ZGAaVXlEEMECPMHr/pub?output=csv", 
+    col_types = cols(GDPM = col_number(), 
+        GDP = col_number(), pop = col_number(), 
+        GDPPC = col_number()))
+
+healthy_data_2 <- healthy_data_dollars %>% 
+  left_join(country_GDP,
+            by = c("City" = "city"))
+
+options(scipen=999)
+
+GDPP_hours <- healthy_data_2 %>% 
+ggplot( aes(x = GDPPC, y = `Hours Worked`, color = `City`)) +
+  geom_point() +
+  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
+       caption = "Data from: ADD LATER",
+       x = "GDP per capita (USD)",
+       y = "Hours Worked (Weekly)",
+       color = "") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "lightblue",
+                                colour = "gray",
+                                size = 0.5,
+                                ),
+        plot.title = element_text(size = 0.05))
+
+ggplotly(GDPP_hours,
+         tooltip = c("text", 
+                     "x",
+                     "City"))
 ```

### 2022-04-28 draft2.Rmd
fixed data issue

@@
 ```{r}
-country_GDP <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQL_6se7aBLQSP92RgP5DkvQ_quTyzsTxskf9ZFpvE_5ifMS5whQ1Lr0JRNMtd1ZGAaVXlEEMECPMHr/pub?output=csv", 
-    col_types = cols(GDPM = col_number(), 
-        GDP = col_number(), pop = col_number(), 
-        GDPPC = col_number()))
-
-healthy_data_2 <- healthy_data_dollars %>% 
-  left_join(country_GDP,
-            by = c("City" = "city"))
-
 options(scipen=999)

### 2022-04-29 draft2.Rmd
Cat alt text

@@
 
-> This graph simply presents reported happiness level against the average weekly hours worked.
+This graph simply presents reported happiness level against the average weekly hours worked.
 Our marked interest in working hours out of all the factors in our initial dataset stems from what we witness each and every day in our lives, communities, and the nation at large.
@@
 
-```{r, fig.width=5, }
+```{r, fig.width=5,fig.alt= "This graph plots various cities as their own color coded dot with a caption when scrolled over.
+Variables happiness and hours worked are on the x and y axes, respectively.
+The captions attached to each point contain happiness level, average weekly hours worked, and the name of the city.
+Following the graph from left to right, a loose trend line appears amongst the points." }
 
@@
 
->Analysis: Can money buy happiness?
+>Concluding Statements: Can money buy happiness?
 Our key findings from this project are ______________.

### 2022-04-29 draft2.Rmd
Added to the data collection section

@@
 - Hours worked info (supplementary source)- [new hours worked data (Penn)](https://worldpopulationreview.com/country-rankings/average-work-week-by-country)
+
+The dataset used was imported from Kaggle.com in a csv file.
+It contains a total of 44 cities, which were selected and ranked by its creator (a U.K.-based company), using 10 different metrics.
+For our study, we decided to focus on two of the variables provided, Happiness Index by country and Hours Worked by city.
+Additionally, we created a new dataset with GDP per capita for each city and made some adjustments to the variables in the original dataset.
+The two were later joined into the final dataset, healthy_data_2.
+
+**Happiness Index**
+
+The “Happiness Levels” variable was taken directly from a specific pillar of the Happy Planet Index, which was generated using survey data from the World Happiness Report.
+The index in our dataset, although reflective of the wellness levels of each country, does not encompass any other poll, leading us to assume the overall happiness of each city.
+The collection of survey data is described on the Happy Planet Index site and consists of asking people to rate their current life on a scale from 0-10.
+Their perception of the best possible life corresponds to a 10 on the scale, and their perception of the worst possible life to a 0.
+The final scores are computed using weighted averages by population and consider the scores from 1-2 years prior to increase the sample size and give more precise estimates.
+The poll gathers around 1,000 responses annually for each country.
 

### 2022-04-29 draft2.Rmd
yay commit!- joce

--- 2022-04-29 draft2.Rmd
@@
     code_download: true
+    code_folding: hide
 ---
@@
 ## Data Collection
-- Healthy living report (main source)- [Healthy Lifestyle Cities Report 2021](https://www.kaggle.com/datasets/prasertk/healthy-lifestyle-cities-report-2021)
-- GDP info (supplementary source)- [GDP data source](https://worldpopulationreview.com/countries/countries-by-gdp)
-- Hours worked info (supplementary source)- [new hours worked data (Penn)](https://worldpopulationreview.com/country-rankings/average-work-week-by-country)
+
+The data set used is titled [Healthy Lifestyle Cities Report 2021](https://www.kaggle.com/datasets/prasertk/healthy-lifestyle-cities-report-2021) and was imported from Kaggle.com in a csv file.
+It contains a total of 44 cities, which were selected and ranked by its creator (a U.K.-based company), using 10 different metrics.
+For our study, we decided to focus on two of the variables provided, happiness index by country and annual hours worked by city.
+We supplemented this data set with a data set we created that included GDP data, population data, and weekly hours worked.
+We gathered our GDP data from the [International Monetary Fund's (IMF) World Economic Outlook database](https://www.imf.org/en/Publications/WEO/weo-database/2018/April).
+The average work week by country data came from an article in the [World Population Review](https://worldpopulationreview.com/country-rankings/average-work-week-by-country) that sourced the data to the Penn World Table 2019 data.
+
+**Happiness Index**
+
+The “Happiness Levels” variable was taken directly from a specific pillar of the [Happy Planet Index](https://happyplanetindex.org/countries/), which was generated using survey data from the [World Happiness Report](https://worldhappiness.report/ed/2021/).
+The collection of survey data is described on the Happy Planet Index site and consists of asking people to rate their current life on a scale from 0-10.
+Their perception of the best possible life corresponds to a 10 on the scale, and their perception of the worst possible life to a 0.
+The final scores are computed using weighted averages by population and consider the scores from 1-2 years prior to increase the sample size and give more precise estimates.
+The poll gathers around 1,000 responses annually for each country.
 
@@
 ```
-Here is a map of the cities included in the analysis. European cities are likely overrepresented because the data was compiled by a UK-based company.  
+
+The following map shows the cities that were chosen in the analysis.
+
 ```{r}
@@
 
-> Because economic performance is a common standard for measuring the success of a given country, we chose to investigate if there is a correlation between gross domestic product (GDP), which is a measure of the total volume of goods and services produced within in country in a given year, and happiness levels as calculated by the **survey**.
-We see that countries with higher GDPPC tend to correlate with higher happiness levels than countries with lower GDPPC.
-We wondered if countries with a higher GDPPC would be more unhappy reflecting that they may work longer hours in order to have such a high level of production.
-It is possible that rather than hours worked, GDP reflects differences in technology, production processes, management, or human capital.
+> “Wealth is like sea-water: The more we drink the thirstier we become; and the same is true of fame.” -Schopenhauer
 
-#GDPPC vs. Hours Worked
 ```{r}
@@
 ggplotly(GDPP_hours,
+         width = 800,
+         height = 430,
          tooltip = c("text", 
@@
 In contrast to our previous analyses, the increased GDP may represent more efficiency of labor, which can sustain the economy with fewer working hours and thus, promote a higher standard of living.
-
-> We chose to investigate if there is a correlation between GDP per capita and happiness levels by country.
-We speculated that countries with a higher GDPPC might be less happy reflecting longer work hours required to maintain such a high level of production.
-On the other hand, higher levels of GDP mirror higher standards of living and higher material wealth which could translate to life satisfaction.
-Overall, we found that countries with higher GDPPC tend to correlate with higher happiness levels than countries with lower GDPPC.
-It is possible that rather than hours worked, GDP reflects differences in technology, production processes, management, or human capital.
 
@@
 
+We chose to investigate if there is a correlation between GDP per capita and happiness levels by country.
+We speculated that countries with a higher GDPPC might be less happy reflecting longer work hours required to maintain such a high level of production.
+However, the GDPPC versus hours worked graph indicated a loose negative relationship between GDPPC and working hours, which seems to imply that people in countries with higher levels of national production actually work less hours.
+This second graph shows that higher levels of GDP appear to correlate to higher life satisfaction.
+This implies that higher standards of living and higher material wealth may translate to more happiness.
+
 > “I think that this is ultimately why we want money: It's to create a world that you prefer." -Hank Green
-
-This graph simply presents reported happiness level against the average weekly hours worked.
-Our marked interest in working hours out of all the factors in our initial dataset stems from what we witness each and every day in our lives, communities, and the nation at large.
-It is easy to assume that those who work less have more time for leisure activities and maintenance of their well-being, and in turn we speculated that fewer weekly work hours would correlate to a greater happiness level.
-However, this graph does not present a strong enough trend to support our hypothesis.
-There is a loose trend, and this can help to give direction to our investigation despite not proving anything for a fact.
-What we DO learn from this graph is the complexity of happiness as a variable.
-Happiness is not only contingent on working hours, but factors such as higher average wages, government investment in citizens and their communities, and access to community resources.
-We recognize that there are cultural, political, and societal nuances that influence whether people work more or less and that different places have different attitudes surrounding work and money.
 
@@
 
-healthy_data_dot <- healthy_data_2 [-c(23),]
+healthy_data_dot <- healthy_data_2 [-c(23),] #Getting rid of Egypt because missing average work week data
 
@@
 ggplotly(Healthy,
+         width = 800,
          tooltip = c("text",
@@
 
-#GDPPC vs.
-Hours Worked (Can we observe a relationship between the GDPC of each contry and the average amount of hours people work per week?) Can the observable patterns tell us something about the contries with low GDPC and a higher number of working hours?
-How can we relate this to happiness?
+This graph simply presents reported happiness level against the average weekly hours worked.
+Our marked interest in working hours out of all the factors in our initial dataset stems from what we witness each and every day in our lives, communities, and the nation at large.
+It is easy to assume that those who work less have more time for leisure activities and maintenance of their well-being, and in turn we speculated that fewer weekly work hours would correlate to a greater happiness level.
+However, this graph does not present a strong enough trend to support our hypothesis.
+There is a loose trend, and this can help to give direction to our investigation despite not proving anything for a fact.
+What we DO learn from this graph is the complexity of happiness as a variable.
+Happiness is not only contingent on working hours, but factors such as higher average wages, government investment in citizens and their communities, and access to community resources.
+We recognize that there are cultural, political, and societal nuances that influence whether people work more or less and that different places have different attitudes surrounding work and money.
 
-```{r}
-options(scipen=999)
-
-GDPP_hours <- healthy_data_2 %>% 
-ggplot( aes(x = GDPPC, y = `Hours Worked`, color = `City`)) +
-  geom_point() +
-  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
-       caption = "Data from: ADD LATER",
-       x = "GDP per capita (USD)",
-       y = "Hours Worked (Weekly)",
-       color = "") +
-  theme(legend.position = "none",
-        panel.background = element_rect(fill = "lightblue",
-                                colour = "gray",
-                                size = 0.5,
-                                ),
-        plot.title = element_text(size = 0.05))
-
-ggplotly(GDPP_hours,
-         tooltip = c("text", 
-                     "x",
-                     "City"))
-```
+> “It is not the man who has too little, but the man who craves more, that is poor.” – Seneca
 

### 2022-04-29 draft2.Rmd
Looks beautiful

@@
 GDPP_hours <- healthy_data_2 %>% 
-ggplot( aes(x = GDPPC, y = `Hours Worked`, color = `City`)) +
-  geom_point() +
+ggplot( aes(x = GDPPC, y = `Hours Worked`)) +
+  geom_point(color = "#3C1518") +
   labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
@@
   theme(legend.position = "none",
-        panel.background = element_rect(fill = "lightblue",
+        panel.background = element_rect(fill = "#FFE5B4",
                                 colour = "gray",
@@
              y = `Avg. Weekly Hours Worked`, 
-             color = `City`)) +
+             color = `Happiness Level`)) +
   geom_point() +
@@
   theme(legend.background = element_blank()) +
-  theme(legend.position = "none")
+  theme(legend.position = "none")+
+  scale_color_gradient(high = "#FFD25A", low = "black")
 
@@
 
->Concluding Statements: Can money buy happiness?
+## Concluding Thoughts
+
+Can money buy happiness?
 Our key findings from this project are ______________.

### 2022-04-29 draft2.Rmd
commit LETS GOOOOOOOOOOOO

@@
 
-```{r}
+```{r, fig.alt = "World map showing 44 cities used in the analysis"}
 labels <- sprintf(
@@
 GDPP_hours <- healthy_data_2 %>% 
-ggplot( aes(x = GDPPC, y = `Hours Worked`)) +
+ggplot( aes(x = GDPPC, y = `Hours Worked`, fill = `City`)) +
   geom_point(color = "#3C1518") +
@@
                      "x",
+                     "y",
                      "City")) 
@@
 
-```{r}
+```{r, fig.alt = "Graph showing gross domestic product (GDP) per capita by country and happiness level.
+Country is mapped on the y-axis and GDP per capita is mapped on the y-axis.
+Switzerland, Ireland, and the United States had the highest GDP per capita and also had high reported happiness levels.
+Countries with higher GDP per capita tend to have higher happiness levels"}
 options(scipen=999)
@@
   geom_point() +
-  labs(title = "Gross Domestic Product per Capita by Country and Happiness Level",
-       caption = "Data from: ADD LATER",
+  labs(title = "GDP per Capita by Country and Happiness Level",
+       caption = "Data from: Healthy Lifestyle Cities Report 2021, IMF World Economic Outlook",
        x = "GDP per capita (USD)",
@@
        (1-10 scale)") +
-  theme(plot.title = element_text(hjust = 1)) +
+  theme(plot.title = element_text(hjust = 0)) +
   theme_classic() +

### 2022-04-29 draft2.Rmd
Added alt text!

@@
 
-```{r}
+```{r, width = 800, fig.alt="This graph shows the relationship between GDP per capita and the number of weekly hours worked in each city.
+The GDPC is represented along the x axis, and the number of hours worked is arranged in increasing order along the y axis.
+When hovering over each individual point, the corresponding city, GDP per capita, and number of hours worked is revealed in a small textbox."}
+
 GDPP_hours <- healthy_data_2 %>% 
@@
   labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
-       caption = "Data from: ADD LATER",
        x = "GDP per capita (USD)",
        y = "Hours Worked (Weekly)",
+       caption = "Data from: Healthy Lifestyle Cities Report 2021, IMF World Economic Outlook",
        color = "") +

### 2022-04-29 draft2.Rmd
Fixed caption

@@
                      "y",
-                     "City")) 
+                     "City")) %>% 
+layout(title = list(text = paste0('Gross Domestic Product per Capita by Country and Average Weekly Hours Worked',
+                                    '<br>',
+                                    '<sup>',
+                                    'Data sourced from Kaggle and World Population Review',
+                                    '</sup>')))
 ```

### 2022-04-29 draft2.Rmd
Concluding Thoughts

@@
 Can money buy happiness?
-Our key findings from this project are ______________.
-We sought to tell a story about the connection between economic prosperity and happiness but with the added factor of working hours.
-Money is inextricable from the work needed to obtain it, and to base our argument purely on GDP or how much money is possessed completely ignores a key factor: how much are people working to obtain said money.
-Thus, we tied the two together, factoring in that having more money likely ______ and working fewer hours means that people will _____________.
-This presents a paradox of sorts, more work generally means more money, and more money means more happiness, but less work also generates more happiness.
-So where is a harmonious balance found?
-We see that ________.
+We sought to tell a story about the connection between economic prosperity and quality of life (most specifically happiness) while keeping in mind the added factor of working hours.
+We found that there is a loose inverse relationship between GDPPC and hours worked, which may highlight differences in technological processes between more and less developed countries.
+GDPPC does not serve as a perfect measure of the prosperity of a country’s people because it is skewed by income inequality and wealth distribution.
+GDPPC gives a near-sighted view of the standard of living in any given country, and it should not be used alone to measure something as qualitative as wellness (or happiness).
+Stressors and work hours are components that are not factored into GDPPC, and higher GDPPC does not even correlate with a greater amount of hours worked.
+This presents a paradox of sorts, it is commonly thought that more work generally means higher income, and higher income leads to more happiness.
+We can infer that less time spent working means increased leisure time which can be spent improving overall health and emotional well-being.
+We also can infer that a certain level of material well-being is necessary because it provides greater access to resources which in turn can boost happiness.
+Economic prosperity and holistic well-being have a reciprocal relationship.
 Our research cannot possibly cover all factors such as access to community programs, optimal living conditions, or types of government and the length to which they go to provide resources.
-All of these ancillary factors play a role in happiness and the ability to work fewer hours, but we posit that looking purely at money and work can still produce illuminating discoveries.
+All of these ancillary factors play a role in happiness and the ability to work fewer hours, but we posit that looking purely at income and hours worked can still produce illuminating discoveries and ideas

### 2022-04-29 finalproject.Rmd
File name change

--- 2022-04-29 draft2.Rmd
@@
 Our research cannot possibly cover all factors such as access to community programs, optimal living conditions, or types of government and the length to which they go to provide resources.
-All of these ancillary factors play a role in happiness and the ability to work fewer hours, but we posit that looking purely at income and hours worked can still produce illuminating discoveries and ideas
+All of these ancillary factors play a role in happiness and the ability to work fewer hours, but we posit that looking purely at income and hours worked can still produce illuminating discoveries and ideas.

### 2022-04-29 finalproject.Rmd
final commit!

@@
     code_download: true
-    code_folding: hide
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
+knitr::opts_chunk$set(echo = FALSE, error=TRUE, message=FALSE, warning=FALSE)
 ```
@@
 The knee-jerk reaction is to emphatically reject a link between life satisfaction and financial abundance because everyone knows both miserable wealthy people and others who appear incredibly joyful despite severe financial difficulties.
-As one rapper (The Notorious B.I.G.) insightfully observed that, “Mo Money Mo Problems,” which illustrates that affluence prompts challenges of its own.
+One rapper (The Notorious B.I.G.) insightfully observed that, “Mo Money Mo Problems,” which illustrates that affluence prompts challenges of its own.
 Some researchers have turned to empirical testing to seek an answer to this question.
 One study by [Jachimowicz](https://www.hbs.edu/ris/Publication%20Files/FinancialScarcity_SPPS_accepted_November1_2021_06f87dd3-4474-4c92-88d1-a5c6b63a2eaa.pdf) and colleagues found that financial instability correlates with higher levels of daily distress.
-Although money alone doesn’t imply happiness, money can eliminate daily hardships that lead to life dissatisfaction.
+Their main finding was that although money alone doesn’t imply happiness, money can eliminate daily hardships that lead to life dissatisfaction.
 A 2010 [Princeton](https://spia.princeton.edu/sites/default/files/content/docs/news/Happiness_Money_Summary.pdf) study measured that a $75,000 annual income was the “sweet spot” for maximizing emotional well-being.
@@
 
-> “Wealth consists not in having great possessions, but in having few wants.” – Epictetus, stoic philosopher
+> “Wealth consists not in having great possessions, but in having few wants.” – Epictetus
 
 Economic performance is a common determinate of standard of living within a country.
-The reasoning goes that a country that functions well economically is able to provide stable income and access to jobs, increase the availability of goods and services, and afford a social safety net.
+The reasoning goes that a country that functions well economically is able to sustain a stable workforce, increase the variety of goods and services available, and afford a social safety net.
 The most common measure of standard of living is gross domestic product (GDP), which is a measure of the total volume of goods and services produced within in country in a given year.
-We paired GDP data with population data to calculate GDP per capita (thereafter, GDPPC) so as to control for differences in population between countries.
+We paired GDP and population data to calculate GDP per capita (thereafter, GDPPC) so as to control for differences in population between countries.
 We believe that GDPPC provides a helpful, though imperfect measure of the standard of living within a country.
@@
 
-The data set used is titled [Healthy Lifestyle Cities Report 2021](https://www.kaggle.com/datasets/prasertk/healthy-lifestyle-cities-report-2021) and was imported from Kaggle.com in a csv file.
-It contains a total of 44 cities, which were selected and ranked by its creator (a U.K.-based company), using 10 different metrics.
-For our study, we decided to focus on two of the variables provided, happiness index by country and annual hours worked by city.
-We supplemented this data set with a data set we created that included GDP data, population data, and weekly hours worked.
+The data set used is titled [Healthy Lifestyle Cities Report 2021](https://www.kaggle.com/datasets/prasertk/healthy-lifestyle-cities-report-2021) and was imported from Kaggle.
+The creator of the data set, a U.K.-based company, included a total of 44 cities which were selected and ranked using 10 different metrics.
+For our study, we decided to focus on two of the variables provided, which were happiness index by country and annual hours worked by city.
+We supplemented this data set with one of our own that included GDP data, population data, and weekly hours worked.
 We gathered our GDP data from the [International Monetary Fund's (IMF) World Economic Outlook database](https://www.imf.org/en/Publications/WEO/weo-database/2018/April).
-The average work week by country data came from an article in the [World Population Review](https://worldpopulationreview.com/country-rankings/average-work-week-by-country) that sourced the data to the Penn World Table 2019 data.
+The average work week by country data came from an article in the [World Population Review](https://worldpopulationreview.com/country-rankings/average-work-week-by-country) that sourced the data from the Penn World Table 2019.
 
@@
             by = c("City" = "city")) %>% 
-  mutate(water_bottle_cost = `Cost of a bottle of water(City)`*1.3,
-         gym_cost = `Cost of a monthly gym membership(City)`*1.3)
+  mutate(water_bottle_cost = `Cost of a bottle of water(City)`* 1.3,
+         gym_cost = `Cost of a monthly gym membership(City)`* 1.3)
 ```
@@
 
-> “Wealth is like sea-water: The more we drink the thirstier we become; and the same is true of fame.” -Schopenhauer
+> “Wealth is like sea-water: The more we drink the thirstier we become.” -Schopenhauer
 
@@
   geom_point(color = "#3C1518") +
-  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
+  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked (hours)",
        x = "GDP per capita (USD)",
-       y = "Hours Worked (Weekly)",
+       y = "",
        caption = "Data from: Healthy Lifestyle Cities Report 2021, IMF World Economic Outlook",
@@
                      "City")) %>% 
-layout(title = list(text = paste0('Gross Domestic Product per Capita by Country and Average Weekly Hours Worked',
+layout(title = list(text = paste0('GDP per Capita by City and Average Work Week (hours)',
                                     '<br>',
                                     '<sup>',
-                                    'Data sourced from Kaggle and World Population Review',
+                                    'Data from: World Population Review, IMF World Economic Outlook',
                                     '</sup>')))
@@
 This initial graph explores the relationship between GDP per capita and the average number of weekly hours worked in each city.
-It allows us to understand what these two factors tell us about the overall well-being of each city later in the study.
 The plot presents a predominantly inverse relationship between GDP per capita and the number of weekly hours worked.
-A cluster of cities is in the range of $0-$20K GDP per capita, and except for one city (Johannesburg), all can be classified as Latin American or Asian.
-We can infer that this relationship may describe different production systems and processes in each country.
-A lower GDP and higher number of hours worked likely points to a lack of access to technological resources or poor organizational management which makes it difficult to increase the standard of living.
-Countries with higher levels of technology can produce the same output as a country with lower levels of technology with much fewer inputs of labor or machinery hours.
-The second observable cluster on this plot is within the bounds of $40K-$60K GDP per capita, with a range of 12.2 between the lowest and highest number of weekly working hours.
-However, most points in the 30-35 weekly working hour range correspond to European cities, which follow the trend of higher GDP per capita and lower working hours.
-In contrast to our previous analyses, the increased GDP may represent more efficiency of labor, which can sustain the economy with fewer working hours and thus, promote a higher standard of living.
+The cluster of cities in the $0-$20K GDPPC range, with the exception of Johannesburg, are all located in either Latin America or Asia.
+We can infer that this relationship may highlight that different geographical regions have different production systems.
+A lower GDP and higher number of hours worked likely points to a lack of access to technological resources or poor organizational management which limits growth of the standard of living.
+Countries with higher levels of technology can produce the same output as countries with lower levels of technology using much fewer inputs of labor or machinery hours.
+The second observable cluster on this plot falls within the bounds of $40K-$60K GDP per capita, with a difference of 12.2 between the lowest and highest number of weekly working hours.
+Most points in the 30-35 weekly working hour range correspond to European cities, which follow the trend of higher GDP per capita and lower working hours.
+In contrast to our previous analyses, the relatively higher GDP may represent more efficient use of labor which can sustain the economy with fewer working hours and promote a higher level of national productivity.
 
@@
 Countries with higher GDP per capita tend to have higher happiness levels"}
-options(scipen=999)
+options(scipen = 999)
 
@@
   theme(plot.title = element_text(hjust = 0)) +
-  theme_classic() +
-  scale_color_gradient(high = "#FFD25A", low = "black")
+  theme_foundation() +
+  scale_color_gradient(high = "#FFD25A", low = "black") +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
 ```
@@
 However, the GDPPC versus hours worked graph indicated a loose negative relationship between GDPPC and working hours, which seems to imply that people in countries with higher levels of national production actually work less hours.
-This second graph shows that higher levels of GDP appear to correlate to higher life satisfaction.
-This implies that higher standards of living and higher material wealth may translate to more happiness.
+This second graph shows that higher levels of GDP appear to correlate with higher life satisfaction.
+This implies that higher standards of living and higher material wealth may translate to more happiness, which could be influenced by lower working hours in these more developed countries.
 
@@
        y = "",
-       caption = "Graph By Cat Terres; data sourced from Kaggle, 
+       caption = "Data sourced from Healthy Lifestyle Cities Report 2021, 
        'Healthy Lifestyle Cities Report 2021'",
@@
   theme_foundation() +
-  theme(legend.title=element_blank())+
+  theme(legend.title = element_blank())+
   theme(legend.background = element_blank()) +
@@
                                     '<sup>',
-                                    'Graph by Cat Terres, data sourced from Kaggle and World Population Review',
+                                    'Data sourced from Healthy Lifestyle Cities Report 2021, World Population Review',
                                     '</sup>')))
@@
 This graph simply presents reported happiness level against the average weekly hours worked.
-Our marked interest in working hours out of all the factors in our initial dataset stems from what we witness each and every day in our lives, communities, and the nation at large.
+Our marked interest in working hours out of all the factors in our initial data set stems from what we witness each and every day in our lives, communities, and the nation at large.
 It is easy to assume that those who work less have more time for leisure activities and maintenance of their well-being, and in turn we speculated that fewer weekly work hours would correlate to a greater happiness level.
-However, this graph does not present a strong enough trend to support our hypothesis.
-There is a loose trend, and this can help to give direction to our investigation despite not proving anything for a fact.
-What we DO learn from this graph is the complexity of happiness as a variable.
-Happiness is not only contingent on working hours, but factors such as higher average wages, government investment in citizens and their communities, and access to community resources.
+However, this graph does not present a strong enough trend to prove our hypothesis.
+What we do learn from this graph is the complexity of happiness as a variable.
+Happiness is not only contingent on working hours, but also on factors such as higher average wages, government investment in citizens and their communities, and access to community resources.
 We recognize that there are cultural, political, and societal nuances that influence whether people work more or less and that different places have different attitudes surrounding work and money.
@@
 GDPPC gives a near-sighted view of the standard of living in any given country, and it should not be used alone to measure something as qualitative as wellness (or happiness).
-Stressors and work hours are components that are not factored into GDPPC, and higher GDPPC does not even correlate with a greater amount of hours worked.
+Other factors such as stressors and work hours are components that are not factored into GDPPC, and higher GDPPC does not even correlate with a greater amount of hours worked.
 This presents a paradox of sorts, it is commonly thought that more work generally means higher income, and higher income leads to more happiness.
@@
 Economic prosperity and holistic well-being have a reciprocal relationship.
-Our research cannot possibly cover all factors such as access to community programs, optimal living conditions, or types of government and the length to which they go to provide resources.
+Our research cannot possibly cover all factors such as access to community programs, optimal living conditions, or types of government and the lengths to which they go to provide resources.
 All of these ancillary factors play a role in happiness and the ability to work fewer hours, but we posit that looking purely at income and hours worked can still produce illuminating discoveries and ideas.
